\textbf{ \Large{Decentralized autonomous sensor fault detection using neural networks}}

### 2015-02-03 Paper/PaperJahrSchlich.tex
Extended section 'Laboratory experiments'
Überarbeitung SHM

@@

Civil engineering structures are exposed to various external impacts during their lifetime. 
Structural health monitoring (SHM) systems can be deployed to evaluate the conditions and to ensure the structural stability of civil engineering structures.
\citet{BisbySHM} defines SHM as "a non-destructive \textit{in-situ} structural evaluation method that uses any of several sensors which are attached to, or embedded in, a structure".
The obtained sensor data is collected by sensor nodes, and then analyzed and stored on a computer system over long periods of time. 
The analysis of the sensor data can reveal abnormal changes in material and geometric behaviour early on.

@@

Over their lifetime, sensors can become inaccurate, faulty, or may even break.
A fault can be defined as a defect of a sensor that leads to an error. An error is the manifestation of a fault---an incorrect system state---that may result in a failure.
To ensure the dependability and the accuracy of the SHM system, sensor faults must be detected and isolated in real time. 
The traditional approach to fault detection is the installation of physically redundant sensors.
Faulty sensors can be identified through the deviation of their measurements from the measurements of correlated sensors.
Physical redundancy, although efficient for sensor fault detection, causes increased installation and maintenance costs due to the multiple installation of sensors. 
Representing a more efficient approach, analytical redundancy typically uses mathematical functions mapping the characteristics of the structure and the correlations of the installed sensors. Virtual sensor measurements are computed for each sensor and then compared to the actual measurements. 
For example, finite element models can be used in combination with data from adjacent sensor nodes to calculate virtual measurements of a sensor
\citep{Smarsly2014}.

In this study, analytical redundancy is implemented into wireless sensor nodes based on artificial neural networks.
Artificial neural networks essentially consist of interconnected data processing units called neurons. 
The neurons are grouped in different layers; usually one input layer, a number of hidden layers, and one output layer.
Artificial neural networks are able to learn, which is achieved by adjusting the weights of the inter-neuron connections until a set of given input variables results in the desired output variables; for example, a neural network can be trained to approximate any mathematical functions with arbitrary accuracy \citep{Li2011}.

@@

\section*{Design and implementation of the wireless structural health monitoring system}
In the following section, the wireless SHM system is introduced and the Java implementation is described.

@@

Tasks 1 to 3 are usually implemented on site, while tasks 4 to 6 are usually implemented on computer systems off site.
A wireless SHM system installed on the building site consists of sensor nodes attached to the construction, a basestation, and a local computer. 
The basestation, which can be an external device or a computer program, links the individual sensor nodes with each other and the local computer.
To each sensor node, several sensors measuring different physical quantities may be connected. 
In this project, the acceleration is measured using wireless sensor nodes and a basestation of the type "Oracle Sun SPOT". 
The 3-axis digital output accelerometer with sensitivity ranging between $\pm$\,2\,g and $\pm$\,8\,g has a maximum sample rate of 125Hz \citep{eDemo2010}.

In operation, the sensor nodes acquire sensor data and may perform initial processing.
The processed data is then transmitted via radio to the local computer, where it is stored for analysis and diagnosis.
In this project, the data is transmitted from the sensor nodes to the basestation by radio, and from the basestation to the local computer via USB cable.
On the computer, the data is stored in a MySQL database.
\todo{Abb}

@@

\autoref{fig:UML} describes the classes of the SHM system code, programmed in Java Platform, Micro Edition. 
The SHM system consists of two packages---\texttt{SensorNode} and \texttt{Basestation}.

The package \texttt{SensorNode} consits of the four classes \texttt{Acceleration\-Sampler}, \texttt{FFT}, \texttt{Communication} and \texttt{MainSpot}, that are embedded directly into the sensor nodes.
The \texttt{AccelerationSampler} class is responsible for measuring the acceleration.
There are two phases: At first, the acceleration is measured with a low samplerate.
Once the acceleration exceeds a threshold, the samplerate is increased and the measured values are stored into an array.
The different phases are indicatad by lighting different LEDs.
The \texttt{FFT} class performs a fast Fourier transform on the measured accelerations. 
With the transformed data, the magnitudes and the correlating frequencies of the oscillation can be calculated.
Finally, the natural frequency can be determined by extracting the maximal magnitude.
\todo{FFT, Magnitude, Frequenz?}
The \texttt{Communication} class opens a radio connection between the sensor node and the basestation and transfers data from the sensor node to the basestation.
The entry point of the programm is the \texttt{startApp()} method in the \texttt{MainSpot} class. 
Within the \texttt{MainSpot} class, instances of the \texttt{Acceleration\-Sampler} class, the \texttt{FFT} class and the \texttt{Communication} class are created to perform the measurement.

The package \texttt{Basestation} runs on the host computer and operates the basestation.
It consists of the classes \texttt{Database\-Handler} and \texttt{MainBase}.
The \texttt{Database\-Handler} class establishes a connection to a database, creates a database table, if none with the specified name is available, and inserts data into the database table.
The entry point of the programm is the \texttt{run()} method in the \texttt{MainBase} class. The \texttt{MainBase} class opens a radio connection between the basestation and the sensor nodes, receives data sent by the sensor nodes and creates an instance of \texttt{Database\-Handler} to insert the data into the database.

>>>>

\usepackage{color}

@@

Civil engineering structures are exposed to various external impacts during their lifetime. 
Structural health monitoring (SHM) systems can be deployed to evaluate the conditions and to ensure the structural stability of civil engineering structures.
\citet{BisbySHM} defines SHM as "a non-destructive \textit{in-situ} structural evaluation method that uses any of several sensors which are attached to, or embedded in, a structure".
The obtained sensor data is collected by sensor nodes, and then analyzed and stored on a computer system over long periods of time. 
The analysis of the sensor data can reveal abnormal changes in material and geometric behaviour at an early stage.

@@

Over \colorbox{cyan}{their} lifetime, sensors can become inaccurate, faulty, or may even break.
A fault can be defined as a defect of a sensor that leads to an error. An error is the manifestation of a fault---an incorrect system state---that may result in a failure.
To ensure the dependability and the accuracy of the SHM system, sensor faults must be detected and isolated in real time. 
\colorbox{cyan}{An often used approach} to fault detection is the installation of physically redundant sensors.
Faulty sensors can be identified through the deviation of their measurements from the measurements of correlated sensors.
Physical redundancy, although efficient for sensor fault detection, causes increased installation and maintenance costs due to the multiple installation of sensors. 
Representing a more efficient approach, analytical redundancy typically uses mathematical functions mapping the characteristics of the structure and the correlations of the installed sensors. Virtual sensor measurements are computed for each sensor and then compared to the actual measurements. 
For example, finite element models can be used in combination with data from adjacent sensor nodes to calculate virtual measurements of a sensor
\citep{Smarsly2014}.

In this study, analytical redundancy is implemented into wireless sensor nodes based on artificial neural networks.
Artificial neural networks essentially consist of interconnected data processing units called neurons. 
The neurons are grouped in different layers; usually one input layer, a number of hidden layers, and one output layer.
Artificial neural networks are able to learn, which is achieved by adjusting the weights of the inter-neuron connections until a set of given input variables results in the desired output variables; for example, a neural network can be trained to approximate any mathematical functions with \colorbox{cyan}{any desired accuracy} \citep{Li2011}.

@@

\section*{Design and implementation of the wireless structural health monitoring system}
In the following section, the wireless SHM system is introduced and \colorbox{cyan}{the} Java implementation is described.

@@

Tasks 1 to 3 are usually implemented on site, while tasks 4 to 6 are usually implemented on computer systems off site.
A wireless SHM system installed on the structure consists of sensor nodes, a basestation, and a local computer. 
The basestation, which can be an external device or a computer program, links the sensor nodes with each other and with the local computer.
To each sensor node, several sensors measuring different physical quantities may be connected. 
In this project, the acceleration is measured using wireless sensor nodes and a basestation of the type "Oracle Sun SPOT". 
The 3-axis digital output accelerometer with sensitivity ranging between $\pm$\,2\,g and $\pm$\,8\,g has a maximum sample rate of 125Hz \citep{eDemo2010}.

\colorbox{cyan}{folgender Absatz geändert:}

During system operation, the sensor nodes acquire acceleration values and perform a fast Fourrier transform to determine the characteristics of the oscillation of the structure.
The processed data is then transmitted via radio to the basestation and, finally, to the local computer, where it is stored in a MySQL database for further analysis and diagnosis.

\todo{Abb}

@@

\autoref{fig:UML} describes the classes of the SHM system code, programmed in Java Platform, Micro Edition. 
The SHM system consists of two packages---\texttt{sensornode} and \texttt{basestation}.

The package \texttt{sensornode} consits of the four classes \texttt{Acceleration\-Sampler}, \texttt{FFT}, \texttt{Communication} and \texttt{MainSpot}, that are embedded directly into the sensor nodes.
The \texttt{AccelerationSampler} class is responsible for measuring the acceleration.
There are two phases: At first, the acceleration is measured with a low samplerate.
Once the acceleration exceeds a threshold, the samplerate is increased and the measured values are stored into an array.
The different phases are indicatad by lighting different LEDs.
The \texttt{FFT} class performs a fast Fourier transform on the measured accelerations. 
With the transformed data, the magnitudes and the correlating frequencies of the measured oscillation can be calculated.
Finally, the natural frequency can be determined by extracting the maximal magnitude.
The \texttt{Communication} class opens a radio connection between the sensor node and the basestation and transfers data from the sensor node to the basestation.
The entry point of the programm is the \texttt{startApp()} method in the \texttt{MainSpot} class. 
Within the \texttt{MainSpot} class, instances of the \texttt{Acceleration\-Sampler} class, the \texttt{FFT} class and the \texttt{Communication} class are created to perform the measurement.

The package \texttt{basestation} runs on the host computer and operates the basestation.
It consists of the classes \texttt{Database\-Handler} and \texttt{MainBase}.
The \texttt{Database\-Handler} class establishes a connection to a MySQL database, creates a database table, if none with the specified name is available, and inserts data into the database table.
The entry point of the programm is the \texttt{run()} method in the \texttt{MainBase} class. The \texttt{MainBase} class opens a radio connection between the basestation and the sensor nodes, receives data sent by the sensor nodes and creates an instance of \texttt{Database\-Handler} to insert the data into the database.
